Epwshiftr: incorporating open data of climate change prediction into \vspace{4pt} building performance simulation for future adaptation and mitigation\\

### 2023-06-29 full-paper/paper.tex
workflow: rerender paper and diff

% add caption for codes
\DeclareNewFloatType{code}{placement=h, fileext=code, name=Listing}
\captionsetup[code]{aboveskip=10pt, belowskip=1pt}

\DefineVerbatimEnvironment{Highlighting}{Verbatim}{%
    commandchars=\\\{\},
    fontsize=\normalsize,
    numbers=left,
    numbersep=5pt
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Please keep the \vspace{4pt} at the top
\title{%
Epwshiftr: incorporating open data of climate change prediction into
\vspace{4pt}
building performance simulation for future adaptation and mitigation\\																								% Line 1
%%% Please keep the \vspace{4pt} between lines in the title
} 																																% Line 2
%If there is no second line then just put \phantom{Line 2} here
%%% Change or delete text before "\\" on the lines below to keep the layout but don't remove the "\\"
%%% Do not exceed more than 6 lines for authors and affiliations
\author{																																														% Line 3
    \phantom{Line 4}\\
  \phantom{Line 5}\\
  \phantom{Line 6}\\
  \phantom{Line 7}\\
  \phantom{Line 8}\\
  \phantom{Line 9}
  } 																																									% Line 9
\date{\vspace{-0.5cm}}	% remove default date and replace the Blank 10th line														% Line 10
%END OF THE TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

\captionof{code}{Install epwshiftr}\label{lst:install}

@@

@@

\captionof{code}{Query ScenarioMIP outputs using the Query Module}\label{lst:index}

@@

\captionof{code}{Summarize the GCM NetCDF files based on the output index}\label{lst:db}

@@

\captionof{code}{Match the global grid points directly using an EPW file and  extract raw GCM data}\label{lst:data}

@@

\captionof{code}{Perform morphing and generate future EPWs}\label{lst:epw}

@@

>>>>

% add caption for codes
\newenvironment{Code}{\captionsetup{type=code}}{}
\DeclareNewFloatType{Code}{placement=h, fileext=code, name=Listing}
\DeclareFloatVCode{beforefloat}{\vspace{2pt}}
\DeclareFloatVCode{afterfloat}{\vspace{-10pt}}
\floatsetup[Code]{capposition=top, captionskip=1pt, precode=beforefloat, postcode=afterfloat}

\DefineVerbatimEnvironment{Highlighting}{Verbatim}{%
    commandchars=\\\{\},
    fontsize=\small,
    numbers=left,
    numbersep=5pt
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Please keep the \vspace{4pt} at the top
\title{%
Epwshiftr: incorporating open data of climate change prediction into
\vspace{4pt}
building performance simulation for future adaptation and mitigation\\																								% Line 1
%%% Please keep the \vspace{4pt} between lines in the title
} 																																% Line 2
%If there is no second line then just put \phantom{Line 2} here
%%% Change or delete text before "\\" on the lines below to keep the layout but don't remove the "\\"
%%% Do not exceed more than 6 lines for authors and affiliations
\author{																																														% Line 3
     Hongyuan Jia\textsuperscript{1} ,  Baisong Ning\textsuperscript{2} \\
  \parbox{\linewidth}{\centering%
     \textsuperscript{1}Chongqing University of Science and Technology, Chongqing, 401331, People's Republic of China \\ \textsuperscript{2}Zhengzhou University, Zhengzhou, Henan Province, 450001, People's Republic of China \\
  }
  \phantom{Line 8}\\
  \phantom{Line 9}
  } 																																									% Line 9
\date{\vspace{-0.5cm}}	% remove default date and replace the Blank 10th line														% Line 10
%END OF THE TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

\begin{Code}
\caption{Install epwshiftr}

\label{lst:install}

@@

\end{Code}

@@

\begin{Code}
\caption{Query ScenarioMIP outputs using the Query Module}

\label{lst:index}

@@

\begin{Code}
\caption{Summarize the GCM NetCDF files based on the output index}

\label{lst:db}

@@

\begin{Code}
\caption{Match the global grid points directly using an EPW file and  extract raw GCM data}

\label{lst:data}

@@

\begin{Code}
\caption{Perform morphing and generate future EPWs}

\label{lst:epw}

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

This study was funded by Research Foundation of Chongqing University of Science
and Technology (project No.~ckrc2021073) and the 111 project (Grant No.~B13041),
The authors also thank the support from the Berkeley Education Alliance for
Research in Singapore (BEARS) for the Singapore-Berkeley Building Efficiency and
Sustainability in the Tropics (SinBerBEST) Program and thank Prof.~Adrian Chong
(National University of Singapore) for his scientific input during epwshiftr
development.
